INTELLIGENT SYSTEMS

### 2021-03-31 paper_3.tex
update paper3

>>>>

\subsubsection{Learning Algotrithm}
In order for both networks to have good training, their parameters must be 
optimized (weights and bias). To achieve this, the following formulas will 
have to be optimized iteratively:
\begin{equation}
    \hat{\theta_1} = \argmin\limits_{\theta_1}||Re(\hat{\theta_2},Cr(\theta_1,x))-x||^2
\end{equation}
\begin{equation}
    \hat{\theta_2} = \argmin\limits_{\theta_2}||Re(\hat{\theta_2},\hat{x}_m)-x||^2
\end{equation}
Where:
\begin{enumerate}
    \item \emph{x} represents the original image
    \item $ \hat{\theta_1} $ and $ \hat{\theta_2} $ are the parameters of \emph{ComcCNN} and \emph{RecCNN}
    \item $ C_r(\cdot) $ and $ R_e() $ represent the \emph{ComcCNN} and \emph{RecCNN}
\end{enumerate}

\subsubsection{Loss Functions}
